Normalization by Evaluation for Call-by-Push-Value and Polarized Lambda-Calculus

### 2019-04-01 fscd19/response-fscd19.txt

Ok, but given the formality of our definitions, the Agda
implementation is a simple exercise.

> 519: What's hard about the agreement proof? Or do you just leave it
> out because you think it's out of scope for the paper?

We are already over the page limit...

> Minor comments
>
> 119: I would maybe write "x : (A ∈ Γ)" to make clear that "x : A ∈ Γ"
> is not a definition here, but you really mean an inhabitant x of a
> type. In named presentations it might be a short hand for "Γ x = A"

WON'T FIX.

>
> 122: Is Cxt a typo? If not, a sentence why Ctx is not used might make
> sense. Is it to avoid confusion with the usual presentation of Ctx
> with arrows inverse to Cxt?

NO COMMENT.

> 146: I would either say "all presheaves will be defined on this and
> this category" or always say which category the presheaf is defined
> on. This makes it way easier for readers to quickly calculate in the
> head that this is really a presheaf.

ADDED. We now say that we only consider presheaves over Ctx^{op}.

> 164: I feel "Needless to say" is unnecessarily snappy to readers with
> only very basic category theory knowledge. As mentioned, your paper is
> doing a really good job in making the presentation accessible, it's a
> good thing that it spells out the details, so I don't think that's
> needless to say at all.

FIXED.

@@

> 178: "an equational theory"

FIXED.

> 201: The symbol for the Kripke function space looks like a hybrid
> between an arrow with a very strange, asymmetric tip and an arrow with
> a hat. I think the latter is intended, so maybe move the hat a little
> bit higher?

FIXED.

@@

> 211: "such an extended context"

FIXED. But was also right before.

> 214: It should be "Ne A Δ"

FIXED. Also A should have been A ⇒ B.

>
> 217: I was confused by the 0 in the index for quite a while. This is a
> singleton context, isn't it? Then maybe write ε.0 or mention that
> singleton contexts look just like types

FIXED.
